Ceph Parallel File System Evaluation Report

### 2013-08-16 ceph-eval.tex
add table of content and list of figures

@@

ORNL at this point was able to both make more client nodes available and also
install a profiling tool called \textbb{perf} that is extremely useful for
profiling both kernel and user space code.  Profiling with perf showed high CPU
utilization on the client due to crc32c processing in the Ceph kernel client. 
Luckily crc32 checksums can be disabled by changing the CephFS mount options:

@@

\section*{Appendix A - CephFS Final Mount Command}

@@

\section*{Appendix B - OSD File System Options}

@@

\section*{Appendix C - CRUSH Map}

@@

\section*{Appendix D - Final ceph.conf}

>>>>

\pagebreak
\thispagestyle{empty}
\tableofcontents

\pagebreak
\thispagestyle{empty}
\listoffigures

\clearpage
\pagenumbering{arabic}

@@

ORNL at this point was able to both make more client nodes available and also
install a profiling tool called \verb!perf! that is extremely useful for
profiling both kernel and user space code.  Profiling with \verb!perf! showed
high CPU utilization on the client due to crc32c processing in the Ceph kernel
client.  Luckily crc32 checksums can be disabled by changing the CephFS mount
options:

@@

\section*{Appendix A - CephFS Final Mount Command}
\addcontentsline{toc}{section}{Appendix A - CephFS Final Mount}

@@

\section*{Appendix B - OSD File System Options}
\addcontentsline{toc}{section}{Appendix B - OSD File System Options}

@@

\section*{Appendix C - CRUSH Map}
\addcontentsline{toc}{section}{Appendix C - CRUSH map}

@@

\section*{Appendix D - Final ceph.conf}
\addcontentsline{toc}{section}{Appendix D - Final ceph.conf}
